surfing

### 2021-08-12 inst/surfing.Rmd
table of number of surfers in the water

The first line shows that, at one of the heats in `wct01`, `Colapinto`
came first, `Bailey` second, and `Wright` came third.  The last line
shows that, at `wct11`, `Ferreira` came first and `Medina` came
second.  We can convert this dataset into a Plackett-Luce likelihood
function but first have to remove the wildcards and also player
`Vries` whose maximum likelihood strength is zero.

>>>>

The first line shows that, at one of the heats in `wct01`, `Colapinto`
came first, `Bailey` second, and `Wright` came third.  The last line
shows that, at `wct11`, `Ferreira` came first and `Medina` came
second.

Following idiom creates a table:

```{r}
table(unlist(lapply(strsplit(jj, " "),length)))
```

This shows that object `jj` has 312 lines of 2 surfers, 160 lines with
3 surfers, 2 lines with 4 surfers, 2 lines with 8 surfers, and one
line with 16 surfers.

We can convert the dataset into a Plackett-Luce likelihood
function but first have to remove the wildcards and also player
`Vries` whose maximum likelihood strength is zero.
